### 2013-07-06 cws/emnlp_cws/discussion.tex
edits to error analysis

Since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems. In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."

%some errors where DD picks the wrong model:
%gold: 有 亭台樓閣 流水
%CRF: 亭台 樓閣  <-- DD
%PCT: 亭台樓閣
\begin{small}
\begin{tabbing}
\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
\> \> joint / military exercises\\
\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\

\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\

\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\

\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
\end{tabbing}
\end{small}
Nevertheless, in many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone. The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.

@@

>>>>

%In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."

%%some errors where DD picks the wrong model:
%%gold: 有 亭台樓閣 流水
%%CRF: 亭台 樓閣  <-- DD
%%PCT: 亭台樓閣
%\begin{small}
%\begin{tabbing}
%\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
%\> \> joint / military exercises\\
%\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%
%\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%\end{tabbing}
%\end{small}
In many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone. The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.

@@

Finally, since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems.
